\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
More pictures and typos work

This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

We are interested in the reduction of the fundamental modules of $\widehat{su(4)}$.
Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}

@@

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}

@@

\section{Conclusion}
\label{sec:conclusion}
We have proved that the injection fan technique can be used to deal with the nonmaximal subalgebras. It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$. The injection fan is formed by the weights $\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+} \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module. This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.

We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems. In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method. This  method is widely used in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.

>>>>

This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

We are interested in the reduction of the fundamental modules of $\hat A_3$.
Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0),\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
  \end{array}
\end{equation}

@@

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}

@@

\section{Conclusion}
\label{sec:conclusion}
We have shown that the injection fan technique can be used to deal with the nonmaximal subalgebras. It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$. The injection fan is formed by the weights $\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+} \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module. This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.

We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems. In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method. This  method is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.

The proposed general approach to the reduction problem has the additional applications in the study of the integrable chains. We will consider those in the upcoming publications.
